Type-safe client-server communication for web applications

### 2014-02-28 paper.tex
Add that "Haste is small and awesome"

This still leaves us with four options: Clean, GHCJS, Haste and UHC. However,
the output from GHCJS is prohibitively large - often in the range of several
megabytes for very simple programs - which rules it out for our use case, in
spite of providing slightly better compatibility with low-level GHC features
than Haste. Similarly, the code produced by the UHC Javascript backend tends to
be relatively slow due to it lacking the more mature optimization capabilities
of GHC, as well as being in the same ballpark as GHCJS for size.\ \cite{haste}

>>>>

This still leaves us with four options: Clean, GHCJS, Haste and UHC. However,
the output from GHCJS is prohibitively large - often in the range of several
megabytes for very simple programs - which rules it out for our use case, in
spite of providing slightly better compatibility with low-level GHC features
than Haste. Similarly, the code produced by the UHC Javascript backend tends to
be relatively slow due to it lacking the more mature optimization capabilities
of GHC, as well as being in the same ballpark as GHCJS for size. Haste, in
contrast, produces code which is generally one to two orders of magnitude
smaller than that produced by GHCJS or UHC.\ \cite{haste}
